Computational methods in landscape ecology

### 2024-06-07 Sections/software.qmd
adds small improvements

### R
<!-- Hesselbarth -->
landscapemetrics
geodiv
vectormetrics
bespatial
motif
?GLCMTextures
?rasterdiv
?terra

@@

GuidosToolbox
?GRASS GIS
?QGIS: LecoS plugin

>>>>

### R
<!-- Hesselbarth -->
<!-- landscapemetrics
geodiv
vectormetrics (also: VecLI -- they mention open source in their paper a few times, but the software seems to be closed source -- https://urbancomp.net/archives/vecliv3beta)
bespatial
LandComp
motif
?GLCMTextures
?rasterdiv
?terra -->

@@

<!-- GuidosToolbox
?GRASS GIS
?QGIS: LecoS plugin -->

### 2024-06-07 Sections/spatial-patterns.qmd
adds small improvements

Moreover, many other entropy-based metrics have been proposed for use in landscape ecology.
The Renyi [@renyiMeasuresEntropyInformation1961] and Gibbs entropies, which are both generalizations of the Shannon entropy, are applied to quantify the complexity of the landscape.
Rao quadratic entropy [@raoDiversityDissimilarityCoefficients1982a] has also been used more in recent years, as it measures not only the relative abundances of elements but also the pairwise dissimilarities or distances between them.<!--https://doi.org/10.1016/j.ecolind.2016.07.039-->
Thus, it can be useful in cases, for example, when the dissimilarities between land cover types, and not only their categories, are relevant.
<!-- more -->

@@

<!-- one/two par about other approaches -->

>>>>

Moreover, many other entropy-based metrics have been proposed for use in landscape ecology.
The Renyi [@renyiMeasuresEntropyInformation1961] and Gibbs entropies, which are both generalizations of the Shannon entropy, are applied to quantify the complexity of the landscape.
Rao quadratic entropy [@raoDiversityDissimilarityCoefficients1982a] has also been used more in recent years, as it measures not only the relative abundances of elements but also the pairwise dissimilarities or distances between them.<!--https://doi.org/10.1016/j.ecolind.2016.07.039-->
Thus, it can be useful in cases, for example, when the dissimilarities between land cover types, and not only their categories, are relevant.
Another recent developement is the use of Kullback-Leibler divergence (also known as relative entropy), which is a measure of the difference between two probability distributions, to describe patterns across scales [@huckebaMultiscaleSpatialEcology2023].

@@

<!-- one/two par about other approaches -->
<!-- e.g., modeling, simulation, prediction, etc. -->
